\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Bacon, Cheddar, and Leek Mini-Quiches}



\subsection*{Ingredients}
$\slfrac{3}{4}$ lb bacon, cut into medium dice\\
3 cups medum-diced leeks, washed and drained\\
1 $\slfrac{1}{4}$ Cups half-and-half\\
1 cup grated extra-sharp cheddar\\
2 large eggs\\
2 large egg yolks\\
2 tablespoons chopped fresh thyme leaves\\
kosher salt and freshly ground black pepper\\
1/4 teaspoon ground nutmeg\\
cooking spray\\
2 1-lb packages frozen puff pastry sheets, thawed\\
all-purpose flour, for rolling\\

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Preheat oven to 400 degrees.
\item In a medium skillet over medium-high heat, cook bacon until browned and crisp, 6 to 8 minutes. Remove from heat and drain. 
\item Save 1-2 T bacon fat in skillet, and cook the leeks over medium heat, stirring occasionally, until softened (about 5 minutes). Let cool slightly.
\item While the leeks cool, combine the half-and-half, cheddar, eggs, egg yolks, thyme, nutmeg, 1 t salt, and 1/2 t pepper in a  medium bowl. Add the leeks and bacon and stir to combine. 
\item Lightly spray 4 12-cup mini muffin tins with cooking spray.  
\item Working with one sheet of puff pastry at a time, use a floured rolling pin to roll the dough into a 10x18 inch rectangle. 
\item Stamp out 3-inch rounds of dough and gently press into the muffin tins, making sure that each round is centered and that the dough extends to the edges of the cup.  
\item Fill each with about 1 T of filling (right to the top of the dough). Repeat with remaining dough and filling until all is used.
\item Position oven racks in top and bottom thirds of oven.
\item Bake quiches, switching position of tins halfway through, for 20 minutes.
\end{list}

\subsection*{Notes}
\begin{itemize}
\item You can bake the quiches immediately, or freeze and bake them later.  To freeze, freeze in muffin tins for about 2 hours, or until set. Remove from tins and transfer to an airtight container, separating layers with plastic wrap.  
\item Frozen quiches should keep for about 1 month.  
\item To bake, put the quiches back into the muffin tins (don't thaw before baking). Bake for 30-35 minutes.
\end{itemize}


\end{document}
