\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Meatloaf Pinwheel}



\subsection*{Ingredients}
\subsubsection*{For the Filling}

1 (10 oz) package frozen chopped spinach - thawed, drained, and squeezed dry\\
1 tablespoon butter\\
1 cup sliced mushrooms\\
$\slfrac{1}{2}$ cup chopped onion\\
$\slfrac{1}{2}$ cup fine dry bread crumbs\\
1 egg\\
$\slfrac{1}{4}$ cup parsley\\
$\slfrac{1}{2}$ teaspoon salt\\
1 pinch ground black pepper\\
1 pinch ground nutmeg\\

\subsubsection*{For the Meatloaf}

1 lb ground beef\\
$\slfrac{1}{2}$ lb ground pork (or turkey)\\
1 cup shredded Cheddar cheese\\
$\slfrac{1}{2}$ cup fine dry bread crumbs\\
1 egg\\
2 teaspoons Worcestershire sauce\\
$\slfrac{3}{4}$ teaspoons salt\\
$\slfrac{1}{4}$ teaspoons freshly ground pepper\\

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Preaheat oven to 350 $\degree$ F.
\item Coarsely chop the spinach and pace in a large bowl; set aside.
\item Heat butter in a large heavy skillet over meadium heat.
\item Sauté mushrooms and onion until onion is translucent.
\item Add mushroom mixture to bowl with spinach.
\item Mix in $\slfrac{1}{2}$ cup bread crumbs, 1 egg, and parsley.  Season with salt, pepper, and nutmeg.
\item In a large bowl, combine ground beef, ground pork (or turkey), Cheddar cheese, $\slfrac{1}{2}$ cup breadcrumbs, and 1 egg.
\item Season with Worcestershire sauce, salt, and pepper.  Mix well.
\item Place meat mixture between two sheets of waxed paper and roll into a rectangle approximately 18x8 inches.
\item Remove top sheet of waxed paper and spread spinach mixture evenly over meat, leaving a $\slfrac{1}{2}$ inch border.
\item Roll up meat from the short end in jelly-roll style, removing paper as you go.
\item Place loaf into an 8x4 inch loaf pan..
\item Bake for about 1 hour, or until browned and juices run clear.
\end{list}

\subsection*{Notes}
\begin{itemize}
\item Meatloaf can be served hot or cold, and will keep in a refrigerator for up to 5 days.
\item Garlic can be added to the mushroom and spinach mixture for a more robust taste.
\item To prevent meatloaf from drying out while cooking, periodically baste it with its own juices.
\item A mixture of $\slfrac{1}{4}$ cup Worcestershire sauce, $\slfrac{1}{8}$ cup Honey, and 2 tablespoons prepared mustard can be used both for basting the meatloaf, and as side when the meatloaf is served.
\end{itemize}

\end{document}
