\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Sausage and Mushroom Frittata}



\subsection*{Ingredients}
$\slfrac{1}{2}$ lb italian sausage\\
2 tbsp olive oil\\
$\slfrac{1}{2}$ lb fresh mushrooms, sliced $\slfrac{1}{4}$ inches thick\\
1 large onion, thinly sliced\\
8 large eggs\\
$\slfrac{1}{2}$ cup whole milk\\
1-5 tbsp flour\\
kosher salt and freshly ground black pepper\\
$\slfrac{1}{2}$ cup grated Pecorino Romano\\
1 tbsp chopped fresh marjoram\\

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}

\item Preheat oven to 350 degrees.  
\item Heat 10-inch oven-proof skillet over medium heat.  
\item Add the sausage and cook, breaking it up with a spoon, until browned.  
\item Add enough olive oil to the fat in the pan to total 2 Tbsp, and add the mushrooms and onions.  
\item Cook, stirring frequently, until the onions are tender and the mushrooms are browned.  
\item Let the mixture cool slightly (it can be warm when added to eggs, but not piping hot.)  
\item In a bowl, whisk the eggs with the whole milk, flour, 1 $\slfrac{1}{2}$ tsp salt, and several grinds of pepper.  
\item Add the sausage, mushrooms, onions, romano cheese, and marjoram, folding them in gently. 
\item Wipe out the skillet, and heat 2 Tbsp olive oil over medium heat.  
\item When the oil is hot, add the egg mixture, spreading everything evenly.  
\item Reduce the heat to low, cover, and cook until the eggs are set about 1 inch from the sides of the pan, 8 to 12 minutes.  
\item Uncover the pan, and transfer the frittata to the oven.  Bake until the top is puffed and completely set, 15 to 25 minutes.  
\item Remove the pan from the oven and run a rubber spatula around the sides of the pan to loosen the frittata.  
Slip it out of the pan and onto a cutting board.  Let the frittata cool for at least 10 minutes before cutting.
\end{list}


\end{document}
