\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Bacon-Wrapped Stuffed Apricots}



\subsection*{Ingredients}
1 cup plus 2 Tbsp granulated sugar
9 oz marcona almonds, coarsely chopped
1 lb bittersweet chocolate, coarsely chopped

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Make the almond brittle:  Line a heavy-duty rimmed baking sheet with foil.  put the sugar in a 2-quart heavy-duty saucepan.  add 1/4 cup watter and swirl to moisten.  cover and boil over high heat until starting to turn golden around the edges, about 4 minutes.  remove the lid and cook, swirling occasionally, until the caramel is deep amber, another 3 to 4 minutes.  stir in half of the nuts.  pour the mixture onto the  foil-covered baking sheet and spread to 1/8 inch thick.  let cool completely at room temperature.  Peel the brittle off the foil, chop coarsely, and sift through a medium-fine sieve to remove the extra-small pieces and brittle dust, which will make the chocolate bark too sweet.  at this piont, you can proceed with making the bark, or store the brittle in an airtight container in the freezer up to one week.  

Make the chocolate bark:  Line two 8-inch-square pans with foil.  in a 12-inch skillet, bring 1 inch of water to a boil over high heat.  reduce the heat to maintain a bare simmer.  put the chocolate in a dry stainless-steel bowl that fits in the skillet and put the bowl in the simmering water bath.  stir unti most of the chocolate is melted, about 5 minutes. Remove the bowl from the water, be careful not to get any waterin the chocolate, and stir until smooth.  Stir in the remaining almonds and the almond brittle.  Divide the chocolate mixture between the prepared pans, making sure that none of the brittle is exposed. (the brittle will sweat and soften if not coated in chocolate.  Shake the pan a little to level the chocolate.  Refrigerate until firm, about 30 minutes.  Turn out the bark and remove the foil.  Cut into small, rustic pieces and refrigerate up to 1 week before serving.
\end{list}


\end{document}