\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Brie, Date, and Toasted Walnut Crostini}



\subsection*{Ingredients}
1 medium baguette, sliced into $\slfrac{1}{2}$ inch rounds\\
2 tablespoon olive oil\\
Kosher salt\\
$\slfrac{1}{2}$ cup coarsely chopped walnuts\\
$\slfrac{1}{2}$ cup Medjool dates pitted and coarsely chopped\\
1 tablespoon honey\\
1 tablespoon balsamic vinegar\\
6 oz. brie, rind trimmed, at room temperature\\
2 tablespoons thinly sliced fresh chives\\

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Position rack in center of oven, and pre-heat to 425$\degree$ F.
\item While oven is pre-heating, toast the chopped walnuts (heat nuts in dry skillet, tossing occasionally, until golden-ground).
\item Set the baguette slices on  large baking sheet.
\item Dab both sides of bread slices with olive oil, and sprinkle one side lightly with salt.
\item Bake until the bread starts to brown and crisp, about 8 minutes.
\item While bread is toasting, toss the walnuts with the dates, honey, and balsamic vinegar.
\item Spread the warm bread slices with brie, then top with the date and nut mixture.
\item Sprinkle with chives, and serve.
\end{list}

\end{document}