\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Ginger Spice Ice Cream}



\subsection*{Ingredients}
4 large egg yolks\\
$\slfrac{3}{4}$ cup plus 1 Tbsp granulated sugar\\
1 $\slfrac{1}{2}$ cups heavy cream\\
1 $\slfrac{1}{2}$ cups whole milk\\
1 $\slfrac{1}{2}$ tsp ground ginger\\
1 tsp ground cinnamon\\
$\slfrac{1}{4}$ tsp ground cloves\\
2 Tbsp molasses\\
1 tsp vanilla extract\\
pinch of table salt\\


\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Set a medium metal bowl in a large bowl of ice water and have a fine sieve at the ready.  
\item Whisk the egg yolks with $\slfrac{1}{4}$ cup of the sugar in a medium heatproof bowl.  
\item Combine the remaining sugar with the heavy cream and milk in a 3-quart saucepan. Set the saucepan over medium 
heat and stir occasionally until the milk is hot but not simmering.  
\item Whisk about $\slfrac{1}{2}$ cup of the hot milk into the yolks and then whisk the yolk mixture back into the milk.  
\item Reduce the heat to medium low and cook, stirring constantly with a clean wooden spoon or rubber spatula, until 
you see whisps of steam and the custard thickens slightly, 3 to 4 minutes.  An instant-read thermometer should register 
170 to 175 degrees.  Don't let the custard overheat or boil, or it will curdle.  
\item Immediately strain the custard through the sieve into the bowl set in the ice-water bath to halt the cooking process.  
\item Sprinkle the ginger, cinnamon, and cloves over the custard while it is still warm and whisk well to distribute evenly.  
\item Wait 10 minutes, and then whisk in the molasses, vanilla, and salt.  
\item Cover the surface of the custard with plastic to prevent a skin from forming and let it cool to room temperature.  
\item Take the bowl out of the water bath and cool thoroughly in the refrigerator (ideally overnight) before freezing.  
Stir the chilled custard to evenly distribute any molasses or spices that may have settled to the bottom.  
\item Freeze in an ice cream maker according to the manufacturers instructinos.  

\end{list}

\subsection*{Notes}
\begin{itemize}
\item With most ice cream makers, the custard will reach its thickest consistency after churning for 30 to 35 minutes.  
However, the ice cream can still be somewhat soft at this point.  If you prefer a firmer consistency, transfer it to a 
covered storage container and freeze until it reaches the desired consistency.  
\item Tightly covered, the ice cream will keep fresh in the freezer for about a week.
\end{itemize}
\end{document}
