\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
\newcommand{\degree}{\ensuremath{^\circ}}

\section*{Spinach, Roasted Red Pepper, and Feta Purses}



\subsection*{Ingredients}
1 $\slfrac{1}{4}$ cups crumbled feta\\
1 tablespoon chopped fresh oregano\\
1 $\slfrac{1}{2}$ teaspoons chopped fresh thyme\\
1 teaspoon grated lemon zest\\
Freshly ground black pepper\\
$\slfrac{1}{2}$ cup unsalted butter\\
1 $\slfrac{1}{2}$ cups thinly sliced scallions\\
Kosher salt\\
$\slfrac{3}{4}$ lb baby spinach, washed and dried\\
1 roasted red pepper, finely diced\\
24 sheets thawed phyllo, 9x14 inches\\

\subsection*{Directions}
\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item Position rack in center of oven, and heat oven to 400 $\degree$ F.
\item In large bowl, combine feta, oregano, thyme, lemon zest, and $\slfrac{1}{2}$ teaspoon black pepper.
\item Melt 2 tablespoons butter in large skillet over medium heat.
\item Add scallions, sprinkle with $\slfrac{1}{4}$ teaspoon salt, and cook, stirring occasionally, until soft and brown in places (about 3 minutes).
\item Add the spinach, sprinkle with a pinch of salt, and cook, tossing, until just wilted.
\item Transfer to a colander to drain and let cool for a few minutes.
\item When cool, thoroughly press and squeeze out any excess liquid.
\item Add spinach and roasted red pepper to the feta mixture and combine well.
\item In a small saucepan, melt the remaining butter. 
\item Line 2 large rimmed baking sheets with parchment paper or brush them with a little of the melted butter.
\item Unroll the phyllo and stack 24 sheets on your work surface.  Cover the stack with plastic wrap and a damp dishtowel. 
\item Take one sheet of phyllo off the stack and lay it on a large cutting board.  Brush with melted butter.  Top with another piece of phyllo 
and brush that piece with butter as well. Repeat with a third piece of phyllo.
\item Cut the stacked, buttered, phyllo sheets in half lengthwise, then cut each half into four even pieces (so you have 8 pieces total).
\item Put 1 heaping tespoon of the feta filling in the center of each piece.  Gather the corners of the phyllo together and pinch together firmly.
\item Transfer the purses to baking sheet, and repeat steps 11 through 13 until all of the phyllo is used (making a total of 48 purses).
\item Bake the purses until phyllo is crisp and browned all over (about 15 to 20 minutes), rotating the pans halfway through to ensure even browning.
\end{list}

\subsection*{Tips}

\begin{itemize}
\item The purses can be made and frozen up to 1 week before baking.  If frozen, purses should be baked straight from the freezer, without thawing first.
\end{itemize}

\end{document}