\documentclass{article}
\usepackage{amsmath,amssymb,verbatim}
\usepackage[right=1in,top=1in,left=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\newcounter{qcounter}
\usepackage{algorithmic}
\usepackage{algorithm}
\begin{document}
\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}

\section*{St Cecilia Society Punch}



\subsection*{Ingredients}
2 medium lemons, thinly sliced\\
$\slfrac{3}{4}$ cup brandy\\
$\slfrac{3}{4}$ cup granulated sugar\\
2 green tea bags\\
$\slfrac{3}{4}$ cup dark rum\\
$\slfrac{1}{2}$ small pineapple, peeled, cored, cut into small $\slfrac{1}{2}$ inch wedges\\
1 750 ml bottle dry sparkling wine, chilled\\
6 cups sparkling water, chilled\\

\subsection*{Directions}
\subsubsection*{The day before}
Put the lemon slices in a large bowl and pour the brandy over them. Let macerate at room temperature overnight.

\subsubsection*{At least 3 hours before serving}

\begin{list}{\arabic{qcounter}:~}{\usecounter{qcounter}}
\item In small saucepan, combine the sugar with $\slfrac{3}{4}$ cups water and bring to a boil over high heat.  Cook, 
stirring occasionally, until sugar dissolves.
\item Remove from heat, add the tea bags, and steep for 2 to 3 minutes.
\item Discard the tea bags and let the syrup cool.
\item Combine the lemons, brandy, syrup, rum, and pineapple in large pitcher or bowl. Chill in refrigerator. 
\end{list}

\subsubsection*{To serve}
Pour the punch into a large, chilled punch bowl with a block of ice.  Add the sparkling wine and sparkling water and stir gently.

\end{document}